\sysfull

### 2018-04-17 paper/implementation.tex
indent

\textbf{New Tasks.} The \texttt{COALA\_TASK} annotation on a function
declaration statically allocates a non-volatile constant variable holding a
task's weight and declares that the function is a task.

\textbf{Task Transitions.} A call to \texttt{COALA\_NEXT\_TASK} immediately
transfers control to a specified next task and can be invoked along
any control path to dynamically determine the next task.
Like prior work~\cite{chain,dino,ratchet}, \sys's control-flow model
assumes that an executing task is not interruptible by asynchronous events.

\textbf{Protected Variables.} The \texttt{COALA\_PV} annotation on a
variable statically allocates and aligns a protected non-volatile variable. The
variable must then be accessed with the \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.

\textbf{Protected Reads and Writes.} The programmer uses the \texttt{RP} and \texttt{WP} API
methods to access protected variables.  These methods cause \sys to find a variable's page.
If the page is not resident in working memory, the method leads to a page fault,
which fetches the page from non-volatile memory. Unlike \texttt{RP},
\texttt{WP} marks the variable's page as dirty, allowing for efficient 
commit back to non-volatile memory.

\textbf{Initialization.} The behavior of the API method
\texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the
addition of performing preliminary kernel initializations, including hardware setup.

@@

\textbf{Execution.} The programmer passes control to \sys's task scheduler 
by calling \texttt{COALA\_RUN} after device initialization. 
%
First the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks. 
%\todo{Go over keywords (coalescing target, current budget, commit phases etc.) and make them consistent with the rest of the paper}{Amjad, Carlo}

>>>>

\noindent\textbf{New Tasks.} The \texttt{COALA\_TASK} annotation on a function
declaration statically allocates a non-volatile constant variable holding a
task's weight and declares that the function is a task.

\noindent\textbf{Task Transitions.} A call to \texttt{COALA\_NEXT\_TASK} immediately
transfers control to a specified next task and can be invoked along
any control path to dynamically determine the next task.
Like prior work~\cite{chain,dino,ratchet}, \sys's control-flow model
assumes that an executing task is not interruptible by asynchronous events.

\noindent\textbf{Protected Variables.} The \texttt{COALA\_PV} annotation on a
variable statically allocates and aligns a protected non-volatile variable. The
variable must then be accessed with the \texttt{RP} and \texttt{WP} API methods at
runtime to ensure correct operation.

\noindent\textbf{Protected Reads and Writes.} The programmer uses the \texttt{RP} and \texttt{WP} API
methods to access protected variables.  These methods cause \sys to find a variable's page.
If the page is not resident in working memory, the method leads to a page fault,
which fetches the page from non-volatile memory. Unlike \texttt{RP},
\texttt{WP} marks the variable's page as dirty, allowing for efficient 
commit back to non-volatile memory.

\noindent\textbf{Initialization.} The behavior of the API method
\texttt{COALA\_INIT} is very similar to \texttt{COALA\_NEXT\_TASK}, with the
addition of performing preliminary kernel initializations, including hardware setup.

@@

\noindent\textbf{Execution.} The programmer passes control to \sys's task scheduler 
by calling \texttt{COALA\_RUN} after device initialization. 
%
First the scheduler updates the coalescing target using the coalescing
strategy.  Second, the scheduler resumes a commit, if one is in progress. Third,
the scheduler clears the list of dirty shadow pages. The scheduler then 
sets the program counter to the next task to run, which \sys tracks in  
non-volatile memory.  
%
Before executing the task, \sys checks whether there is a partially committed
task to resume, which requires \sys to restore volatile state, including the program
counter.  
%
If there is no in-progress, partially committed task, \sys starts executing and
coalescing tasks. 
%\todo{Go over keywords (coalescing target, current budget, commit phases etc.) and make them consistent with the rest of the paper}{Amjad, Carlo}
